Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-19 WSSSPE2_report/WSSSPE2_review.tex
Section 11: touch up.

WSSSPE has developed an engaging online mechanism via the online social network
Twitter (hashtag ``\#WSSSPE''). There were substantially more tweets (messages) during
WSSSPE2 than WSSSPE1 or WSSSPE1.1. The WSSSPE community counts 178 tweets and
61 followers between May 16, 2013 and April 18, 2015. Some tweets were re-tweeeted or liked more than the others.
Table~\ref{tab:tweets} summarizes the top tweets and their statistics on the day of workshop, Nov 16, 2014,
reverberating some of the main points and highlights in the meeting.

>>>>

WSSSPE has developed an engaging online mechanism via the online social network
Twitter (hashtag ``\#WSSSPE''). There were substantially more tweets (messages)
during WSSSPE2 than WSSSPE1 or WSSSPE1.1. Some of the main points and highlights
in the meeting reverberated in Twitter. Table~\ref{tab:tweets} summarizes the
top tweets happened on the day of workshop, Nov 16, 2014,
